TacticToe: Learning the Game of Tactics

### 2018-01-12 tactictoe_jv.tex
better affiliations

\institute{Cezary Kaliszyk \at
Department of Computer Science, University of Innsbruck,
%Technikerstr. 21a/2,
Innsbruck, Austria\\ \url{bla@bla}
\and
Karol Pak \at Institute of Informatics, University of Bialystok, Bialystok, Poland\\\url{bla@bla}}

>>>>

\institute{Thibault Gauthier and Cezary Kaliszyk \at
Department of Computer Science, University of Innsbruck,
%Technikerstr. 21a/2,
Innsbruck, Austria\\ \url{{thibault.gauthier,cezary.kaliszyk}@uibk.ac.at}
\and
Josef Urban \at Czech Technical University, Prague\\\url{josef.urban@gmail.com}
\and Ramana Kumar and Michael Norrish \at Data61}
